Psych 254 Replication Project Analysis

### 2016-04-27 analysis.Rmd
auc + infrastructure

```{r}
library(dplyr)
library(ggplot2)
library(googlesheets)
```

@@

```{r}
project_plan_sheet <- gs_url("https://docs.google.com/spreadsheets/d/1KZw75xlypvtK0cDoOHqXfFd3HsrfJ4gbq8iEJ6LOa0Y")
project_plan <- gs_read_csv(project_plan_sheet)
```

>>>>

Libraries.

```{r}
library(dplyr)
library(ggplot2)
library(googlesheets)
library(readr)
```

@@

```{r}
project_plan_sheet <- gs_url("https://docs.google.com/spreadsheets/d/1KZw75xlypvtK0cDoOHqXfFd3HsrfJ4gbq8iEJ6LOa0Y")
project_plan_raw <- gs_read_csv(project_plan_sheet)
```

Exclude those to be excluded.

```{r}
project_plan <- project_plan_raw %>%
  filter(`Include in final writeup?`==1) 
```
